COG-ED Manuscript

### 2022-01-07 06_Paper/COG-ED/Manuscript.Rmd
removed subheadings
made BF ttests paired

## Effort discounting and Need for Cognition

@@

## Revising the COG-ED paradigm

@@

## Hypotheses

Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with n-back level.
Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
Here we added they hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.

@@

@@

  hypothesis1a_BF <- anovaBF(formula = dprime ~ level, data = h1a_data, progress = FALSE)
  hypothesis1a_contrasts$BF10 <- c(extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 3], y = h1a_data$dprime[h1a_data$level == 4], progress = FALSE))$bf)

@@

  hypothesis1b_BF <- anovaBF(formula = medianrt ~ level, data = h1b_data, progress = FALSE)
  hypothesis1b_contrasts$BF10 <- c(extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 3], y = h1b_data$medianrt[h1b_data$level == 4], progress = FALSE))$bf)

@@

  hypothesis1c_mental_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 3], y = h1c_data$mental[h1c_data$level == 4], progress = FALSE))$bf)

@@

  hypothesis1c_physical_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE))$bf)

@@

  hypothesis1c_time_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 3], y = h1c_data$time[h1c_data$level == 4], progress = FALSE))$bf)

@@

  hypothesis1c_performance_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 3], y = h1c_data$performance[h1c_data$level == 4], progress = FALSE))$bf)

@@

  hypothesis1c_effort_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE))$bf)

@@

  hypothesis1c_frustration_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 3], y = h1c_data$frustration[h1c_data$level == 4], progress = FALSE))$bf)

@@

  hypothesis2a_BF <- anovaBF(formula = sv ~ level, data = h2a_data, progress = FALSE)
  hypothesis2a_contrasts$BF10 <- c(extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 2], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 3], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 4], progress = FALSE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 3], y = h2a_data$sv[h2a_data$level == 4], progress = FALSE))$bf)

>>>>

@@

@@

Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013], and detailed in the attached design table..
Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with n-back level.
Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
Here we added they hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.

@@

The results of each analysis will be assessed on the basis of both *p*-value and the Bayes factor $BF10$.

@@

  hypothesis1a_BF <- anovaBF(formula = dprime ~ level, data = h1a_data, progress = FALSE)
  hypothesis1a_contrasts$BF10 <- c(extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 3],
                                                     progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 3], y = h1a_data$dprime[h1a_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf)

@@

  hypothesis1b_BF <- anovaBF(formula = medianrt ~ level, data = h1b_data, progress = FALSE)
  hypothesis1b_contrasts$BF10 <- c(extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 3],
                                                     progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 3], y = h1b_data$medianrt[h1b_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf)

@@

  hypothesis1c_mental_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 2],
                                                            progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 3], y = h1c_data$mental[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf)

@@

  hypothesis1c_physical_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 2],
                                                              progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf)

@@

  hypothesis1c_time_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 2],
                                                          progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 3], y = h1c_data$time[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf)

@@

  hypothesis1c_performance_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 2],
                                                                 progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 3], y = h1c_data$performance[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf)

@@

  hypothesis1c_effort_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2],
                                                            progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf)

@@

  hypothesis1c_frustration_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 2],
                                                                 progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 3], y = h1c_data$frustration[h1c_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf)

@@

  hypothesis2a_BF <- anovaBF(formula = sv ~ level, data = h2a_data, progress = FALSE)
  hypothesis2a_contrasts$BF10 <- c(extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 2],
                                                     progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 3],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf,
                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 3], y = h2a_data$sv[h2a_data$level == 4],
                                                   progress = FALSE, paired = TRUE))$bf)
